\thetitle

### 2021-05-31 writing/discussion.tex
minor fix

An investigation of these empty blame cases reveals problems with tracking blame
for higher-order functions, but conversely suggests three improvements for the
Transient algorithm. To illustrate, consider the call \texttt{(filter f xs)}.
The first suggestion is that the blame map should know that inputs to
\texttt{f} may have come from the \texttt{xs} list; concretely, the blame-map
entry for \texttt{f} should point to \texttt{xs} as a parent.
Second, there should be two parents for \texttt{f} instead of one, because
both \texttt{xs} and \texttt{filter} are responsible for sending correct input
to \texttt{f}. Third, the blame map should work equally well in programs
that rename \texttt{filter} or that replace the identifier with
an expression. This third point suggests a need for type-like specifications
that guide the construction of the blame map, instead of the identifier-based
matching in Reticulated~\cite{vss-popl-2017} and Shallow Racket.

>>>>

An investigation of these empty blame cases reveals problems with tracking blame
for higher-order functions and conversely suggests three improvements for the
Transient algorithm. To illustrate, consider the call \texttt{(filter f xs)}.
The first suggestion is that the blame map should know that inputs to
\texttt{f} may have come from the \texttt{xs} list; concretely, the blame-map
entry for \texttt{f} should point to \texttt{xs} as a parent.
Second, there should be two parents for \texttt{f} instead of one, because
both \texttt{xs} and \texttt{filter} are responsible for sending correct input
to \texttt{f}. Third, the blame map should work equally well in programs
that rename \texttt{filter} or that replace the identifier with
an expression. This third point suggests a need for type-like specifications
that guide the construction of the blame map, instead of the identifier-based
matching in Reticulated~\cite{vss-popl-2017} and Shallow Racket.
